Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural music skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-04-19 introduction/Subsections/Assumptions.tex
Updates from Overleaf

This thesis posits that high-level musical concepts manifest over time and remain invariant to specific attributes such as tonal quality, tempo, key, orchestration, signal noise, and others. This is akin to a sheet music composition being performed in myriad ways using diverse instruments and styles while preserving its core essence.

Abstract features, such as melody, harmony, rhythm, tempo, form, and expression, can be identified irrespective of waveform or production style. This approach offers an objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.

Although a waveform might have a limited number of sheet music representations that accurately encapsulate its musical components, a single sheet music composition can be performed infinitely using various instruments, voices, tempos, and interpretations. The distinct tonal quality of a waveform is significantly influenced by the specific instrument or production technology employed in its creation, complicating the transcription of its sonic properties into precise sheet music notation.

@@

>>>>

This thesis posits that high-level musical concepts manifest over time and remain invariant to specific attributes such as tonal quality, tempo, key, orchestration, signal noise, etc. This is akin to a sheet music composition performed in myriad ways using diverse instruments and styles while preserving its essence.

Abstract features, such as melody, harmony, rhythm, tempo, form, and expression, can be identified irrespective of waveform or production style. This approach offers objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.

Although a waveform might have limited sheet music representations that accurately encapsulate its musical components, a single sheet music composition can be performed infinitely using various instruments, voices, tempos, and interpretations. The distinct tonal quality of a waveform is significantly influenced by the specific instrument or production technology employed in its creation, complicating the transcription of its sonic properties into precise sheet music notation.

@@

\begin{figure}[h]
\includegraphics[clip,width=\columnwidth]{figures/images/sheet1.png}% 
\caption{\small{XXXX}}
\label{fig: Sheet music aug 1}
\end{figure}

\begin{figure}[h]
\includegraphics[clip,width=\columnwidth]{figures/images/sheet2.png}% 
\caption{\small{XXXX}}
\label{fig: Sheet music aug 2}
\end{figure}

\begin{figure}[h]
\includegraphics[clip,width=\columnwidth]{figures/images/sheet3.png}% 
\caption{\small{XXXX}}
\label{fig: Sheet music aug 3}
\end{figure}

\begin{figure}[h]
\includegraphics[clip,width=\columnwidth]{figures/images/sheet4.png}% 
\caption{\small{XXXX}}
\label{fig: Sheet music aug 4}
\end{figure}
